Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-23 doc/PRF2022/Supplementary.tex
removed word 'ordinate'
finished up my changesg

\noindent
%{\label{MovieS6}\bf JP Vesicle in a Taylor-Green Flow with Various
%$\lambda$ Values}: 
{\label{MovieS6}\bf JP Vesicle in Various Taylor-Green Flows}: A
circular vesicle bilayer is placed in a Taylor-Green flow. The parameter
$\lambda$ controls the TG cell size and the values are varied from 1~nm
to 4~nm while the flow rate is chosen so that
$\lambda\dot\gamma=0.1$~nm/ns. The parameter $\lambda$ determines the
steady-state polygonal tank-treading shape. The rotation direction is
clockwise for $\lambda=1$~nm and $\lambda=2$~nm, and counterclockwise
for $\lambda=3$~nm and $\lambda=4$~nm. Streamlines of the flow are
included.

@@

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and
striated JP configurations under shear flow (Supplementary
Figures~\ref{fig:ulshraw}--\ref{fig:stshraw}) and under TG flow
(Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$, panels
(b) for alignment $S_2$, and panels (c) are for strain $E$ (as a
percentage).  A common ordinate is used for each of the respective
panels to facilitate comparison between data sets. 
%\newpage

>>>>

\noindent
%{\label{MovieS6}\bf JP Vesicle in a Taylor-Green Flow with Various
%$\lambda$ Values}: 
{\bf JP Vesicle in Various Taylor-Green Flows}: A circular vesicle
bilayer is placed in a Taylor-Green flow. The parameter $\lambda$
controls the TG cell size and the values are varied from 1~nm to 4~nm
while the flow rate is chosen so that $\lambda\dot\gamma=0.1$~nm/ns. The
parameter $\lambda$ determines the steady-state polygonal tank-treading
shape. The rotation direction is clockwise for $\lambda=1$~nm and
$\lambda=2$~nm, and counterclockwise for $\lambda=3$~nm and
$\lambda=4$~nm. Streamlines of the flow are included.

@@

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and
striated JP configurations under shear flow (Supplementary
Figures~\ref{fig:ulshraw}--\ref{fig:stshraw}) and under TG flow
(Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$, panels
(b) are for alignment $S_2$, and panels (c) are for strain $E$ (as a
percentage). The same vertical and horizontal axes are used for each of
the respective panels to facilitate comparison between data sets. 
%\newpage
